ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-05-06 paper.tex
We did it (again)!!

%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you,huang2017speed} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture. 
%that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.

@@

Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD, YOLO and MobileNet~\cite{liu2016ssd,redmon2018yolo,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models. 
%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
%This leads to model that uses much less memory, but again with a small drop in accuracy.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}

>>>>

%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture. 
%that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.

@@

Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy tradeoff, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models. 
%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
%This leads to model that uses much less memory, but again with a small drop in accuracy.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}
